---
title: "CLV_DESCRIPTIVE"
author: "Ariana Arellano"
date: "`r Sys.Date()`"
output: html_document
---


```{r}
#install.packages("tidyverse")
#install.packages("tidyr")
#install.packages("haven")
library(tidyverse)
library(tidyr)
library(haven)
library(ggplot2)
library(glmnet)
```
#Importing File
```{r}
path <- file.path("~/Library/Mobile Documents/com~apple~CloudDocs/MSBA CPP/Capstone Project/CLV_PROJ_2023-MAIN R/THREE.sav")
dataset <- read_sav(path)
```

```{r}
# Create a summarized data frame with the total number of orders and total number of mailings for each unique value in targmail
df_summary <- dataset %>%
  group_by(targmail) %>%
  summarize(total_orders = sum(targords))

# Bar chart with swapped axes
ggplot(df_summary, aes(x = targmail, y = total_orders)) +
  geom_bar(stat = "identity", fill = "blue") +
  xlab("Number of Prom 85 Mailings Sent") +
  ylab("Number of Prom 85 Orders Placed") +
  ggtitle("Relationship between Mailings Sent and Prom 85 Orders") +
  theme_minimal()
```

```{r}
library(ggplot2)

# Create a summarized data frame with the total number of orders, total number of mailings, and sales for each unique value in targmail
df_summary <- dataset %>%
  group_by(targmail) %>%
  summarize(total_orders = sum(targords),
            total_sales = sum(targamnt))

# Create a bar chart for the relationship between mailings and orders
bar_chart <- ggplot(df_summary, aes(x = targmail, y = total_orders)) +
  geom_bar(stat = "identity", fill = "blue") +
  xlab("Number of Prom 85 Mailings Sent (targmail)") +
  ylab("Number of Prom 85 Orders Placed (targords)") +
  ggtitle("Prom 85 Orders per Mailng") +
  theme_minimal()

# Create a scatter plot for the distribution of sales and orders
scatter_plot <- ggplot(dataset, aes(x = targords, y = targamnt)) +
  geom_point() +
  xlab("Number of Prom 85 Orders Placed (targords)") +
  ylab("Prom 85 Sales Amount (targamnt)") +
  ggtitle("Prom 85 Sales per Order") +
  theme_minimal()

# Arrange the charts side by side
library(gridExtra)
grid.arrange(bar_chart, scatter_plot, ncol = 2)
```

```{r}
library(ggplot2)
library(dplyr)

# Histogram for the distribution of orders placed
hist_orders <- ggplot(dataset, aes(x = targords)) +
  geom_histogram(binwidth = 1, fill = "green", alpha = 0.7) +
  xlab("Number of Prom 85 Orders Placed") +
  ylab("Frequency") +
  ggtitle("Distribution of Orders Placed") +
  theme_minimal()

# Histogram for the distribution of sales amount
hist_sales <- ggplot(dataset, aes(x = targamnt)) +
  geom_histogram(binwidth = 100, fill = "blue", alpha = 0.7) +
  xlab("Prom 85 Sales Amount") +
  ylab("Frequency") +
  ggtitle("Distribution of Sales Amount") +
  theme_minimal()

# Print the histograms
print(hist_orders)
print(hist_sales)
```

```{r}
library(ggplot2)
library(dplyr)

# Apply logarithmic transformation to the data
dataset$log_targords <- log(dataset$targords)
dataset$log_targamnt <- log(dataset$targamnt)

# Create histograms for the transformed data
hist_log_orders <- ggplot(dataset, aes(x = log_targords)) +
  geom_histogram(binwidth = 0.2, fill = "green", alpha = 0.7) +
  xlab("Log of Number of Orders Placed") +
  ylab("Frequency") +
  ggtitle("Distribution of Log Orders Placed") +
  theme_minimal()

hist_log_sales <- ggplot(dataset, aes(x = log_targamnt)) +
  geom_histogram(binwidth = 0.2, fill = "blue", alpha = 0.7) +
  xlab("Log of Prom 85 Sales Amount") +
  ylab("Frequency") +
  ggtitle("Distribution of Log Sales Amount") +
  theme_minimal()

# Print the histograms
print(hist_log_orders)
print(hist_log_sales)
```

```{r}
hist_sales <- ggplot(dataset, aes(x = targamnt)) +
  geom_histogram(binwidth = 100, fill = "blue", alpha = 0.7) +
  xlab("Prom 85 Sales Amount (targamnt)") +
  ylab("Frequency") +
  ggtitle("Distribution of Sales Amount") +
  theme_minimal()

# Logarithmic transformation
dataset$log_targamnt <- log(dataset$targamnt)

# Histogram for the distribution of log-transformed sales amount
hist_log_sales <- ggplot(dataset, aes(x = log_targamnt)) +
  geom_histogram(binwidth = 0.2, fill = "green", alpha = 0.7) +
  xlab("Log of Prom 85 Sales Amount (targamnt)") +
  ylab("Frequency") +
  ggtitle("Distribution of Log Sales Amount") +
  theme_minimal()

# Arrange histograms side by side
side_by_side <- grid.arrange(hist_sales, hist_log_sales, ncol = 2)

# Print the side-by-side histograms
print(side_by_side)
```

```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)

# Histogram for the distribution of total sales
hist_totsale <- ggplot(dataset, aes(x = totsale)) +
  geom_histogram(binwidth = 100, fill = "blue", alpha = 0.7) +
  xlab("Total Sales Amount (totsale)") +
  ylab("Frequency") +
  ggtitle("Distrib. of Total Sales Amount") +
  theme_minimal()

# Logarithmic transformation
dataset$logtotsale <- log(dataset$totsale)

# Histogram for the distribution of log-transformed total sales
hist_logtotsale <- ggplot(dataset, aes(x = logtotsale)) +
  geom_histogram(binwidth = 0.2, fill = "green", alpha = 0.7) +
  xlab("Log of Total Sales Amount (totsale)") +
  ylab("Frequency") +
  ggtitle("Distrib. of Log Total Sales Amount") +
  theme_minimal()

# Arrange histograms side by side
side_by_side_totsale <- grid.arrange(hist_totsale, hist_logtotsale, ncol = 2)

# Print the side-by-side histograms for total sales
print(side_by_side_totsale)
```

```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)

# Histogram for the distribution of total sales
hist_totord <- ggplot(dataset, aes(x = totord)) +
  geom_histogram(binwidth = 100, fill = "blue", alpha = 0.7) +
  xlab("Total Order Amount (totord)") +
  ylab("Frequency") +
  ggtitle("Distrib. of Total Order Amount") +
  theme_minimal()

# Logarithmic transformation
dataset$logtotord <- log(dataset$totord)

# Histogram for the distribution of log-transformed total sales
hist_logtotord <- ggplot(dataset, aes(x = logtotord)) +
  geom_histogram(binwidth = 0.2, fill = "green", alpha = 0.7) +
  xlab("Log of Total Order Amount (totord)") +
  ylab("Frequency") +
  ggtitle("Distrib. of Log Total Order Amount") +
  theme_minimal()

# Arrange histograms side by side
side_by_side_totord <- grid.arrange(hist_totord, hist_logtotord, ncol = 2)

# Print the side-by-side histograms for total sales
print(side_by_side_totord)
```

```{r}
library(ggplot2)

ggplot(dataset, aes(x = logtotord, y = logtotsale)) +
  geom_point(color = "blue") +
  labs(x = "Log Total Orders", y = "Log Total Sales") +
  ggtitle("Relationship between Log Total Orders and Log Total Sales")
```
##Create avgsale variable
```{r}
totsale <- dataset$totsale
totord <- dataset$totord

small_positive_value <- 1e-6
totsale[totsale <= 0] <- small_positive_value
totord[totord <= 0] <- small_positive_value

logtotsale <- log(totsale)
logtotord <- log(totord)

avgsale <- logtotsale/logtotord
```

##Mutate original dataset to create log totsale and log totord columns
```{r}
library(dplyr)

# Assuming dataset is your original dataset
dataset <- dataset %>%
  mutate(log_totsale = log(totsale),
         log_totord = log(totord))
```
###There were NaN's produced so we took the mean of each column to replace NaN's
```{r}
library(dplyr)

# Assuming dataset is your original dataset
dataset <- dataset %>%
  mutate(log_totsale = ifelse(is.nan(log_totsale), mean(log_totsale, na.rm = TRUE), log_totsale),
         log_totord = ifelse(is.nan(log_totord), mean(log_totord, na.rm = TRUE), log_totord))
```

##Add avgsale to original dataset
```{r}
# Assuming dataset is your original dataset
dataset <- dataset %>%
  mutate(avgsale = log_totsale / log_totord)
```

##Testing if there are missing values or inifinte values in avgsale
```{r}
# Check for missing values
missing_values <- sum(is.na(dataset$avgsale))

# Check for infinite values
infinite_values <- sum(is.infinite(dataset$avgsale))

if (missing_values > 0) {
  cat("There are missing values in avgsale.\n")
}

if (infinite_values > 0) {
  cat("There are infinite values in avgsale.\n")
}
```
##There were infinite values so replaced them with a small value
```{r}
# Check for zero values in totord
zero_denominator <- sum(dataset$totord == 0)

if (zero_denominator > 0) {
  cat("There are zero values in totord. You may need to handle these cases.\n")
}

# Add a small constant to denominator to avoid division by very small numbers
small_constant <- 1e-6  # Choose an appropriate small value

dataset <- dataset %>%
  mutate(avgsale = totsale / (totord + small_constant))
```

#Quadratic Regression Model
##Fit a quadratic model to the data and view summary
```{r}
# Fit a quadratic regression model
model <- lm(avgsale ~ log_totord + I(log_totord^2), data = dataset)

# Display the model summary
summary(model)
```

